### 2015-10-10 README.Rmd
updated readme
cleaned up readme some more

High quality companies are likely outperform the market, while ``junk'' companies are likely to underperform.

@@

##Updating your Data
If you're interested in inputting your own data, you can generate financial statements for a data frame of companies as follows:

```{r}
#companies #Your custom data frame of company names and tickers. The column name for tickers must be "ticker"
#rawdata <- get_info(companies) #Retrieves raw financial statements from google finance through the quantmod package.
#financials <- tidyinfo(rawdata) #Renders raw data in a format usable by other functions in this package.
```

get_info temporarily saves your progress to the extdata folder at all stages of its process, allowing you to resume your downloading if the process is interrupted for any reason.

###Updating Prices
Updating prices is a separate, lengthy process, and for that reason is separated from the other functions that automatically collect financial statements. To update prices, which is necessary for calculating safety measurements, call:

```{r}
# rawprices <- get_prices(companies) #Retrieves stock price data from Google Finance for listed companies for the past two years. Also saves data from the S&P 500, retrieved from Yahoo Finance.
# prices <- tidy_prices(rawprices) #Renders the raw data into a form usable by other functions in this package.
```

>>>>

High quality companies are likely outperform the market, while "junk" companies are likely to underperform.

@@

##Updating your Data
Suppose you want to use the qmj package for your a custom set of companies, a dataset we will call "custom_companies". You can generate the most recent financial statements for those companies as follows:

```{r}
# Note that your custom data frame of company names and tickers must have the column name "ticker" for the column of tickers.

## Retrieves raw financial statements from google finance through the quantmod package.

rawdata <- get_info(companies)

## Renders raw data in a format usable by other functions in this package and also dramatically improves readability.

financials <- tidyinfo(rawdata)

```

get_info also allows you to resume your downloading if the process is interrupted for any reason.

##Updating Prices
Updating prices is a separate, lengthy process, and for that reason is separated from the other functions that automatically collect financial statements. To update prices, which is necessary for calculating safety measurements, call:

```{r}

## Retrieves stock price data from Google Finance for listed companies for the past two years. Also saves data from the S&P 500, retrieved from Yahoo Finance.

rawprices <- get_prices(companies)

## Renders the raw data into a form usable by other functions in this package.

prices <- tidy_prices(rawprices) 
```
